|

### 2021-07-27 prova_knit_finale.Rmd
small change

    \item it is not clear that what is optimal at time $t$ remains such at future stages. In other words, it is not truly clear how the minimization of the variance of the inferential weights at each stage affect the efficiency of the PF estimators;

>>>>

    \item it is not clear that what is optimal at time $t$ remains such at future stages. In other words, it is not truly clear how the minimization of the variance of the inferential weights at each stage affects the efficiency of the PF estimators;
